---
title: "Russian Troll Tweets"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    smooth_scroll: true
    storyboard: true

---

```{r setup, include=FALSE}
library(tidyverse)
library(inspectdf)
library(skimr)
library(ggthemes)
#install.packages("usethis")
library(usethis)
# create www folder
fs::dir_create("www/")
# options for chunks
knitr::opts_chunk$set(
  cache = FALSE,
  echo = TRUE,
  collapse = FALSE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE,
  dev = "ragg_png",
  out.width = '85%',
  fig.path = "www/",
  dpi = 320,
  fig.align = "center",
  fig.width = 7,
  fig.height = 5.5,
  fig.retina = 2
  )
# tibble printing
options(
  scipen = 99999,
  pillar.print_max = 10, 
  pillar.print_min = 10)
options(repos = "https://cloud.r-project.org")

```






Background {.storyboard}
===========================================================

### Info {data-commentary-width=350}



Original paper on Russian Troll Tweets:

*Why We’re Sharing 3 Million Russian Troll Tweets*
Oliver Roeder. [PloS ONE](https://fivethirtyeight.com/features/why-were-sharing-3-million-russian-troll-tweets/)




*** 

Additional links or sources... 

*Troll Factories: The Internet Research Agency and State-Sponsored Agenda Building*
Darren L. Linvill. (http://pwarren.people.clemson.edu/Linvill_Warren_TrollFactory.pdf)
*

### Packages {data-commentary-width=350}


The Russian Troll Tweets data set comes from the ['fivethirtyeight' github repo](https://github.com/fivethirtyeight/russian-troll-tweets.git). You can install it by using the code below:


```{r install_russiantrolltweets, eval=FALSE}
install.packages("fivethirtyeight")
# or
# install.packages("remotes")
remotes::install_github("fivethirtyeight")

```



Code for obtaining data...

```{r}
```

*** 

Information about the dataset...



Import {.storyboard}
===========================================================

### Import {data-commentary-width=300}

The complete data set contains three million tweets. For the sake of storage we pulled 1,000 tweets from three different sub sets of data to work with. 

```{r import-tweet-6, echo=FALSE}

tweet_6_raw <- readr::read_csv(file = "https://raw.githubusercontent.com/fivethirtyeight/russian-troll-tweets/master/IRAhandle_tweets_6.csv", n_max = 1000)
```

```{r glimpsetweet6raw}
glimpse(tweet_6_raw)
```

```{r import-tweet-1, echo=FALSE}
tweet_1_raw <- readr::read_csv(file = "https://raw.githubusercontent.com/fivethirtyeight/russian-troll-tweets/master/IRAhandle_tweets_1.csv", n_max = 1000)
```

```{r glimpsetweet1raw}
glimpse(tweet_1_raw)
```



```{r import-tweet-9, echo=FALSE}
tweet_9_raw <- readr::read_csv(file = "https://raw.githubusercontent.com/fivethirtyeight/russian-troll-tweets/master/IRAhandle_tweets_9.csv", n_max = 1000)
```


```{r glimpsetweet9raw}
glimpse(tweet_9_raw)
```




### Skim {data-commentary-width=400}

```{r echo=FALSE}
skimr::skim(tweet_1_raw) |> 
  tibble::as_tibble()

```

```{r echo=FALSE}
skimr::skim(tweet_6_raw) |> 
  tibble::as_tibble()

```

```{r echo=FALSE}
skimr::skim(tweet_9_raw) |> 
  tibble::as_tibble()

```

Visualize {.storyboard}
===========================================================

### Numeric {data-commentary-width=400}

Code for creating graphs...

```{r inspect_num,echo=FALSE}
tweet_6_raw %>% 
  select(-contains("_id")) %>% 
inspect_num(df1 = . ) %>%
  show_plot(text_labels= TRUE) +
  ggthemes::theme_fivethirtyeight(base_size = 8)
```


### Types {data-commentary-width=400}

```{r inspect_types,echo=FALSE}

inspect_types(df1 = tweet_6_raw) %>% 
  show_plot(text_labels= TRUE, plot_type=3) +
  ggthemes::theme_wsj(base_size = 8)

```


### Character {data-commentary-width=400}


```{r inspect_cat,echo=FALSE}
#names(tweet_6_raw)
tweet_6_raw %>% 
  select(-article_url, -content, -harvested_date, -publish_date, -starts_with("tco")) %>% 
inspect_cat(df1 = .) %>%
  show_plot(text_labels= TRUE)
ggthemes::theme_solarized(base_size=8)
```


***






### Future Work


